---
title: "Plotting"
author: "Bulun Te"
date: "2024-02-16"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message=FALSE, warning=FALSE}

# Load the library  
# Load data

library(tidyverse)
library(lubridate)
library(circular)
library(reshape2)
library(patchwork)
library(GGally)

# Set working directory to the project root
if (!requireNamespace("here", quietly = TRUE)) {
  install.packages("here")
}
library(here)
setwd(here())

source("EDA_func.R")

# set default language and time zone
Sys.setenv(LANGUAGE = "en")
Sys.setlocale("LC_TIME", "en_US.UTF-8")

load("GroupData.RData")

```

```{r}

summary_bulun = data_bulun %>% select(Total.ST.min,
                      Pickups,
                      Duration.per.use,
                      Steps,
                      Temperature_F,
                      Snow) %>% psych::describe() %>% as.data.frame()

summary_xin = data_xin %>% select(Total.ST.min,
                      Pickups,
                      Duration.per.use,
                      Steps,
                      Temperature_F,
                      Snow) %>% psych::describe() %>% as.data.frame()

summary_zhang = data_zhang %>% select(Total.ST.min,
                      Pickups,
                      Duration.per.use,
                      Steps,
                      Temperature_F,
                      Snow) %>% psych::describe() %>% as.data.frame()

summary_all = data_merge %>% select(Social.ST.min,
                      Pickups,
                      Duration.per.use,
                      Steps,
                      Temperature_F,
                      Snow) %>% psych::describe() %>% as.data.frame() %>% write.csv("summary.csv")

# rbind(summary_bulun,summary_xin,summary_zhang) %>% write.csv("summary.csv")


```


# Time Series Plot

```{r}

B_plot = ggplot(data = data_bulun ,aes(x=Date, y=Social.ST.min)) + 
  geom_line() + 
  geom_smooth(method = "gam")+
  labs(title="Bulun's Social Screen Time", x="Date", y="Social ST min")

X_plot = ggplot(data = data_xin ,aes(x=Date, y=Social.ST.min)) +
  geom_line() + 
  geom_smooth(method = "gam")+
  labs(title="Xinwei's Social Screen Time", x="Date", y="Social ST min")+
  theme_minimal()

Z_plot = ggplot(data = data_zhang ,aes(x=Date, y=Social.ST.min)) +
  geom_line() + 
  geom_smooth(method = "gam")+
  labs(title="Zhang's Social Screen Time", x="Date", y="Social ST min")+
  theme_minimal()

B_plot + X_plot + Z_plot + plot_layout(ncol = 3)


```

Time series plots shows that three time series have different trends. Bulun's time series has a increasing trend, Xinwei's time series has a almost constant trend and Zhang's time series has a decreasing trend.


## ACF plot for Social Screen Time


```{r,fig.width=15, fig.height=5}

par(mfrow=c(1,3))

acf(data_bulun$Social.ST.min, lag.max = 15, main = "ACF for Social Screen Time for Student 1")
acf(data_xin$Social.ST.min, lag.max = 15, main = "ACF for Social Screen Time for Student 2")
acf(data_zhang$Social.ST.min, lag.max = 15, main = "ACF for Social Screen Time for Student 3")

```

ACF plots shows that time series of student 2 almost does not have autocorrelation.



```{r}

Box.test(data_bulun$Social.ST.min, lag = 1, type = "Ljung-Box")

Box.test(data_zhang$Social.ST.min, lag = 11, type = "Ljung-Box")

```

Result of Ljung-Box test shows that there is no autocorrelation in the time series of student 3. However, there is autocorrelation in the time series of student 1. 




## Circular plot for Pickup.1st

```{r,fig.width=20, fig.height=20}

png("circular_plot.png", width=20, height=20, units="in", res=500)

par(mar=c(0.1,0.1,1,15),
        mfrow=c(3,2),
    cex=1.1)

circular_plot(data_bulun,"Student 1")
circular_plot(data_xin,"Studetn 2")
circular_plot(data_zhang,"Student 3")
dev.off()

```


## Violin plot for Social Screen Time grouped by stayup

```{r,fig.width=15, fig.height=10}

violin_bulun = violin_plot(data_bulun,"Student 1",trim = TRUE)

violin_xin = violin_plot(data_xin,"Student 2")

violin_zhang = violin_plot(data_zhang,"Student 3")


occu_bulun = plot_occupation_time_curve(data_bulun, "Social.ST.min", "Semester", c(1, 0), c("blue", "red"),"Student 1")
occu_xin = plot_occupation_time_curve(data_xin, "Social.ST.min", "Semester", c(1, 0), c("blue", "red"),"Student 2")
occu_zhang = plot_occupation_time_curve(data_zhang, "Social.ST.min", "Semester", c(1, 0), c("blue", "red"),"Student 3")

violin_bulun+violin_xin+violin_zhang+occu_bulun+occu_xin+occu_zhang+plot_layout(ncol = 3)



```


```{r,fig.width=15, fig.height=7}

# taken in the report

g_bulun = plot_heatmap(data_bulun, "Student 1")
g_xin = plot_heatmap(data_xin, "Student 2")
g_zhang = plot_heatmap(data_zhang, "Student 3")

g_bulun+g_xin+g_zhang+plot_layout(ncol = 3)

```


```{r,fig.width=16, fig.height=14}

plot_pairwise(data_xin, "Student 2")
plot_pairwise(data_bulun, "Student 1")
plot_pairwise(data_zhang, "Student 3")


```


## Weather grouped by stay up

```{r,fig.width=15, fig.height=6}

g_xin = plot_occupation_time_curve(data_xin, "Temperature_F", "Stay.late", c(1, 0), c("blue", "red"),"Student 2")
g_bulun = plot_occupation_time_curve(data_bulun, "Temperature_F", "Stay.late", c(1, 0), c("blue", "red"),"Student 1")
g_zhang = plot_occupation_time_curve(data_zhang, "Temperature_F", "Stay.late", c(1, 0), c("blue", "red"),"Student 3")

g_bulun+g_xin+g_zhang+plot_layout(ncol = 3)

```

```{r,fig.width=15, fig.height=6}

g_xin = plot_occupation_time_curve(data_xin, "Steps", "Stay.late", c(1, 0), c("blue", "red"),"Student 2")
g_bulun = plot_occupation_time_curve(data_bulun, "Steps", "Stay.late", c(1, 0), c("blue", "red"),"Student 1")
g_zhang = plot_occupation_time_curve(data_zhang, "Steps", "Stay.late", c(1, 0), c("blue", "red"),"Student 3")

g_xin+g_bulun+g_zhang+plot_layout(ncol = 3)

```














